Glyph-maps for visualizing climate data and models

### 2011-09-23 paper.tex
fixes to irregular data plots

\subsection{Irregular locations}
Figure \ref{fig:irregular} shows linear trends for monthly average surface temperature at stations in the USHCN (Version 2) ground station network.  It illustrates three challenges in working with irregular locations: there is no natural choice for icon size, icons can potentially overlap, and comparisons rely more heavily on the reference guides.  The icon sizes were chosen manually for these two plots, although the icons are displayed at about the same size, they correspond to XX degrees and YY degrees square respectively in the geographical coordinates. 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.4\linewidth]{ghcn-mountains}%
  \includegraphics[width=0.6\linewidth]{usa-lin-overlap}%
  \caption{Glyph-maps of ground station temperature values, 2001-2010, for the mountain states and the entire United States.} % these aren't actually plotting the same thing.
  \label{fig:irregular}
\end{figure}
The two panels illustrate one approach to the overlapping problem: zooming.  There is an interplay between icon size (in geographical units), plotting area (in geographical units) and plot size (in display units).  Icons need to be big enough to be readable on the display, but small enough to avoid overlapping.  Readability can be maintained and overlapping reduced by decreasing the icon size and simultaneously increasing the display size or decreasing the plotting area.  However, there are generally limitations in display size (or resolution) and the utility of plotting very small areas.

>>>>

\subsection{Irregular locations}
Figure \ref{fig:irregular} shows linear trends for monthly average surface temperature at stations in the USHCN (Version 2) ground station network.  It illustrates three challenges in working with irregular locations: there is no natural choice for icon size, icons can potentially overlap, and comparisons rely more heavily on the reference guides.  The icon sizes were chosen manually for these two plots, although the icons are displayed at about the same size, they correspond to 1 degrees and 0.5 degrees square respectively in the geographical coordinates. 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.55\linewidth]{usa-lin-overlap}%
  \includegraphics[width=0.35\linewidth]{ghcn-mountains}%
  \caption{Glyph-maps of the linear trend in ground station temperature values, 1950-2010, of all continental US USHCN stations (left) and stations in the mountain states (right).} 
  \label{fig:irregular}
\end{figure}
The two panels illustrate one approach to the overlapping problem: zooming.  There is an interplay between icon size (in geographical units), plotting area (in geographical units) and plot size (in display units).  Icons need to be big enough to be readable on the display, but small enough to avoid overlapping.  Readability can be maintained and overlapping reduced by decreasing the icon size and simultaneously increasing the display size or decreasing the plotting area (as done in the right panel in Figure \ref{fig:irregular}).  However, there are generally limitations in the maximum display size (or resolution) and the utility of plotting very small areas.
